---
title: "EDA and Data Scrubbing Bank Data"
author: "Deboleena"
date: "March 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
bankDirty <- read.csv("C:/Users/Deboleena/OneDrive - Southern Methodist University/Desktop/MSBA/Fall/Mod B/Data Mining/Assignment data/Homework1/bankDirty.csv", stringsAsFactors = FALSE)

```
No of rows and columns in th data set. Structure of data frame.
```{r}
rows <- nrow(bankDirty)
rows
columns <- ncol(bankDirty)
columns
str(bankDirty)
```
Variables and their types in data frame
```{r}
lapply(bankDirty, class)
```
```{r}
numeric_rows <- bankDirty[,unlist(lapply(bankDirty, is.numeric))]
summary(numeric_rows)
```
Checking for outliers and changing them to missing
Plot data with outliers
```{r}
outlierVar <- which(sapply(bankDirty,is.numeric))
bankDirty[,outlierVar] <- data.frame(lapply(bankDirty[outlierVar], function(x) {
  ifelse((x < 0) | x > (mean(x, na.rm = TRUE) + 3*sd(x, na.rm = TRUE)), NA, x) }))
summary(bankDirty)
bankDirty_1 <- bankDirty
```


Imputing unkown and missing values with NA in categorical variables
```{r}
bankDirty <- bankDirty_1
bankDirty[,-outlierVar] <- unlist(lapply(bankDirty[,-outlierVar], function(x) {
  ifelse((x == "unknown") | (x == ""),NA,x)
  }))
```
categorical variables after imputing with NAs
```{r}
bankDirty[,-outlierVar] <- lapply(bankDirty[,-outlierVar], as.factor)

```
Correlation of all numerical columns 
Correlation in all numeric columns

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
# base  R solution
p1 <- ggplot(bankDirty, aes(x=bankDirty$age)) +
  geom_histogram(breaks=seq(0, 100, by =2),fill="blue", color="black")+
  labs(title="Age histogram plot",x="age", y = "Count")+
  theme_classic()

p2 <- ggplot(bankDirty, aes(x=bankDirty$balance)) +
  geom_histogram(fill="blue", color="black")+
  labs(title="Balance histogram plot",x="balance", y = "Count")+
  theme_classic()
p3 <- ggplot(bankDirty, aes(x=bankDirty$duration)) +
  geom_histogram(fill="blue", color="black")+
  labs(title="Duration histogram plot",x="balance", y = "Count")+
  theme_classic()
p4 <- ggplot(bankDirty, aes(x=bankDirty$campaign)) +
  geom_histogram(fill="blue", color="black")+
  labs(title="Campaign histogram plot",x="balance", y = "Count")+
  theme_classic()
p5 <- ggplot(bankDirty, aes(x=bankDirty$pdays)) +
  geom_histogram(fill="blue", color="black")+
  labs(title="pdays histogram plot",x="balance", y = "Count")+
  theme_classic()
p6 <- ggplot(bankDirty, aes(x=bankDirty$previous)) +
  geom_histogram(fill="blue", color="black")+
  labs(title="Previous histogram plot",x="balance", y = "Count")+
  theme_classic()
grid.arrange(p1, p2, p3, p4, p5, p6, ncol=2)

```

```{r}
q1 <- ggplot(bankDirty, aes(x=job))+
  geom_bar(stat="count", width=0.7, fill="steelblue")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

q2 <- ggplot(bankDirty, aes(x=marital))+
  geom_bar(stat="count", width=0.7, fill="steelblue")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

q3 <- ggplot(bankDirty, aes(x=education))+
  geom_bar(stat="count", width=0.7, fill="steelblue")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
q4 <- ggplot(bankDirty, aes(x=y))+
  geom_bar(stat="count", width=0.7, fill="steelblue")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) 
grid.arrange(q1, q2, q3, q4, ncol = 2)
```

```{r message=FALSE, warning=FALSE}
library(wordcloud)
library(tm)
library(RColorBrewer)
wordcloud(bankDirty$job, max.words = 100, random.order = FALSE)
```


